Fast Algorithms for Intersection of Non-matching Grids Using \plucker Coordinates.

### 2016-11-30 paper_intersections.tex
Fix notation in proof of barycentric coords.
Make the proof of barycentric coordinates clearer.

\subsection{Intersection Line-Triangle (1d-2d)}
\label{sec:1d-2d}
Let us consider a line $p$ with parametric equation 
\begin{equation}
    \label{eq:line_parametric}
    \vc X = \vc A + t\vc u,
\end{equation}
on which a line segment $S_1$ is defined by $t\in [0,1]$ and a triangle $S_2$ given by vertices $(\vc V_0, \vc V_1, \vc V_2)$ 
with oriented sides $s_i=(\vc V_j, \vc V_k)$, $j=(i+1)\text{ mod }3$, $k=(i+2)\text{ mod }3$. 
\begin{lemma}
The permuted inner products $\pi_p \odot \pi_{s_i},\, i=0,1,2$ have the same non-zero sign if and only if there
is an intersection point $\vc X$ on the $p$ and inside the triangle $S_2$. 
The barycentric coordinates of $\vc X$ on $S_2$ are
\begin{equation}
  \label{eq:bary_centric}
   w_i = \frac{\pi_p \odot \pi_{s_i}}{ \sum_{j=0}^{2} \pi_p \odot \pi_{s_i} }.
\end{equation}
\end{lemma}
\begin{proof}
Using the barycentric coordinates the intersection point can be expressed as $\vc X = \vc V_0 + w_1 \vc s_2 - w_2 \vc s_1$.
The line $p$ has \plucker coordinates $(\vc u, \vc u \times \vc X)$ since these are invariant to change of the initial point. 
Combining these two expressions we get
\[
   \pi_p \odot \pi_{s_1} = \vc u \cdot (\vc s_1 \times \vc V_2) + \vc s_1 \cdot ( \vc u \times [\vc V_0 + w_1\vc s_2 - w_2 \vc s_1])
   =-w_1 \vc u \cdot (\vc s_1 \times \vc s_2).
\]
Since $\vc s_0 + \vc s_1 + \vc s_2=0$ we have $ \vc s_1 \times \vc s_2 = \vc s_2 \times \vc s_0 = \vc s_0 \times \vc s_1$ and thus
\[
   \pi_p \odot \pi_{s_i} = -w_i \vc u \cdot (\vc v_1 \times \vc v_2).
\]
The point $\vc X$ is inside $S_2$ if and only if $w_i>0$ for all $i=0,1,2$.
\end{proof}
Having the barycentric coordinates of $\vc X$ on $S_2$, we can compute also its local coordinate on $p$ from its parametric form:
\begin{equation}
   \label{eq:line}
   X_i  = A_i + t u_i, \text{ for } i=1,2,3
\end{equation}
We use $i$ with maximal $|u_i|$ for practical computation.

>>>>

\subsection{Intersection Line-Triangle (1d-2d)}
\label{sec:1d-2d}
Let us consider a line $p$ with parametric equation 
\begin{equation}
    \label{eq:line_parametric}
    \vc X = \vc A + t\vc u,
\end{equation}
on which a line segment $S_1$ is defined by $t\in [0,1]$ and a triangle $S_2$ given by vertices $(\vc V_0, \vc V_1, \vc V_2)$ 
with oriented sides $s_i=(\vc V_j, \vc V_k)$, $j=(i+1)\text{ mod }3$, $k=(i+2)\text{ mod }3$.
\notePE{I think adding figure with node and side numbering would make it easier to read.}
\begin{lemma}
The permuted inner products $\pi_p \odot \pi_{s_i},\, i=0,1,2$ have the same non-zero sign if and only if there
is an intersection point $\vc X$ on the $p$ and inside the triangle $S_2$. 
The barycentric coordinates of $\vc X$ on $S_2$ are
\begin{equation}
  \label{eq:bary_centric}
   w_i = \frac{\pi_p \odot \pi_{s_i}}{ \sum_{j=0}^{2} \pi_p \odot \pi_{s_i} }.
\end{equation}
\end{lemma}
\begin{proof}
Using the barycentric coordinates, the intersection point can be expressed as $\vc X = \vc V_0 + w_1 \vc s_2 - w_2 \vc s_1$.
The line $p$ has \plucker coordinates $(\vc u, \vc u \times \vc X)$ since these are invariant to change of the initial point. 
Combining these two expressions and substituing for $\vc V_0-\vc V_2=\vc s_1$, we get for side $\vc s_1$
\[
   \pi_p \odot \pi_{s_1} = \vc u \cdot (\vc s_1 \times \vc V_2) + \vc s_1 \cdot ( \vc u \times [\vc V_0 + w_1\vc s_2 - w_2 \vc s_1])
   =-w_1 \vc u \cdot (\vc s_1 \times \vc s_2).
\]
Since $\vc s_0 + \vc s_1 + \vc s_2=0$ we have $ \vc s_1 \times \vc s_2 = \vc s_2 \times \vc s_0 = \vc s_0 \times \vc s_1$ and thus
\begin{eqnarray}
   \pi_p \odot \pi_{s_i} &=& -w_i \vc u \cdot (\vc s_1 \times \vc s_2), \label{eq:bary_centric_part1}\\
   \sum_{i=0}^{2} \pi_p \odot \pi_{s_i} &=& - \vc u \cdot (\vc s_1 \times \vc s_2). \label{eq:bary_centric_part2}
\end{eqnarray}
The result \eqref{eq:bary_centric} then follows directly from combination of \eqref{eq:bary_centric_part1} and \eqref{eq:bary_centric_part2}.
The point $\vc X$ is inside $S_2$ if and only if $w_i>0$ for all $i=0,1,2$.
\end{proof}
Having the barycentric coordinates of $\vc X$ on $S_2$, we can compute also its local coordinate on $p$ from its parametric form:
\begin{equation}
   \label{eq:line}
   X_i  = A_i + t u_i, \text{ for } i=1,2,3
\end{equation}
We use $i$ with maximal $|u_i|$ for practical computation.
